Project Protocol

### 2019-10-18 protocol.Rmd
new title
flip direction of nwse

#	Title
Assessing the effectiveness of visualisation methods for spatial distributions affected by small areas with high population densities.

@@

#	Data management and record keeping
As the data will be held publicly online, it will be accessible under a license for people to reuse. It will also be held accessible to QUT researchers

##	Confidentially and privacy
All data will be deidentified, there is no need to protect confidentiality when the data has been anonymised.

##	Data security
All the survey information will be stored on github, a publicly available site, as well as on site at QUT.

##	Record retention
The records of data and analysis undertaken will be stored on github as well as on site at QUT.

##	Secondary use 
The analysis scripts and the data collected will be available for secondary use. Thisn their consent form. will be disclosed to participants

>>>>

#	Title
Assessing the effectiveness of hexagon tile maps for communicating spatial distributions of disease for Australia.

@@

#	Data management and record keeping

During the project, datasets produced from the project and that are approved for public access will be made available via QUT's Research Data Finder. These will be deidentified and require only the necessary answers for the research to be reproducible.

##	Confidentially and privacy
Datasets produced from the project and that will not be available for public access will contain demographic information about the participants. If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.

##	Data security

Responses to the survey will be stored securely using a private google drive accessible only to the researchers during the study through their password protected google drive accounts. This will contain potentially identifiable information if the respondents provide personal demographic information.

##	Record retention

To ensure records are retained during and following the study the responses will be stored on the google drive immediately following the submission by participants. At the conclusion of the survey, the data will remain in the password protected google drive account.

During the analysis phase the researchers Stephanie and Dianne will make copies of the survey responses to their work devices (laptop computers), that are password protected.

This data set will also be deidentified and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations. 
The records of data analysis undertaken and the deidentified data will be stored on github as well as on QUT network drives.

##	Secondary use

The analysis scripts and the data collected will be available for secondary use by other researchers to reproduce these results and also be used in future studies. This will be communicated to participants in their consent form.
